### 2018-02-08 master/paper.tex
Fix typo

\section*{International Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada and Takuya Azumi,
    ``TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems,''
    \emph{In Proceedings of the IEEE 14th International Conference on Embedded Software and Systems (ICESS)},
    2017.
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Lightweight Ruby Framework for Improving Embedded Software Efficiency,''
    \emph{In Proceedings of the 4th IEEE International Conference on Cyber-Physical Systems, Networks, and Applications (CPSNA)},
    pp. 71-76, 2016.
\end{enumerate}

\section*{Domestic Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``Componentized Dynamic Memory Allocator for Embedded Systems,''
    \emph{In Proceedings of IPSJ Kansai-Branch Convention 2017},
    A-3, 2017 (in Japanese).
\item
    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
    ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
    \emph{In Proceedings of ETNET2016},
    No.8, pp.1-6, 2016 (in Japanese).
\end{enumerate}

>>>>

\section*{International Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
    ``TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems,''
    \emph{In Proceedings of the IEEE 14th International Conference on Embedded Software and Systems (ICESS)},
    2017.
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Lightweight Ruby Framework for Improving Embedded Software Efficiency,''
    \emph{In Proceedings of the 4th IEEE International Conference on Cyber-Physical Systems, Networks, and Applications (CPSNA)},
    pp. 71-76, 2016.
\end{enumerate}

\section*{Domestic Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Componentized Dynamic Memory Allocator for Embedded Systems,''
    \emph{In Proceedings of IPSJ Kansai-Branch Convention 2017},
    A-3, 2017 (in Japanese).
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
    \emph{In Proceedings of ETNET2016},
    No.8, pp.1-6, 2016 (in Japanese).
\end{enumerate}
